\section{Related Work}

\paragraph{Traditional Smart Contract Analysis.}
Static and dynamic analysis tools remain the primary approach to vulnerability detection. Slither \citep{feist2019slither} performs dataflow analysis, Mythril \citep{mueller2017mythril} uses symbolic execution, and Securify \citep{tsankov2018securify} employs abstract interpretation. While these tools achieve reasonable precision on well-defined vulnerability classes, empirical evaluations reveal significant false positive rates and limited coverage of complex semantic flaws \citep{durieux2020empirical}.

\paragraph{LLM-Based Vulnerability Detection.}
Recent work explores LLMs for smart contract analysis. GPTLens \citep{hu2023gptlens} introduces an adversarial framework using LLMs as both auditor and critic, while PropertyGPT \citep{liu2024propertygpt} combines retrieval-augmented generation with formal verification. Fine-tuned models achieve over 90\% accuracy on benchmarks \citep{hossain2025leveraging}, though performance degrades substantially on real-world contracts \citep{ince2025gendetect}.

\paragraph{Benchmark Datasets.}
SmartBugs Curated \citep{ferreira2020smartbugs} provides 143 annotated contracts serving as a standard evaluation dataset, while SolidiFI \citep{ghaleb2020solidifi} uses bug injection to create controlled samples. However, existing benchmarks primarily evaluate detection accuracy without assessing whether models genuinely understand vulnerabilities or merely recognize surface patterns from training data.

\paragraph{LLM Robustness and Memorization.}
Distinguishing memorization from reasoning has emerged as a critical evaluation challenge. Recent work demonstrates that models remain highly sensitive to input modifications, with performance drops of up to 57\% on paraphrased questions \citep{sanchez2025none}. \citet{wu2024reasoning} show that LLMs often fail on counterfactual variations of tasks they solve in canonical form, suggesting reliance on memorized patterns. Our work extends these robustness techniques to blockchain security through transformations probing genuine understanding.
